Verifying Demonstrations

### 2019-02-06 paper/ZKPK-instantiations.tex
Changes set notation (\Z -> \ZZ), removes DBIV
Edits ZKPK-instantiations
Minor cosmetic fixes for ZKPK-instantiations
Sets anon-cred, ZKPK figures on page-of-floats (in appendix)
Replaces \paragraph with \subsubsection where necessary

\subsubsection{Instantiations of the \acs{ZKPK} protocols}

\NewAlgorithm{\PKprove}{PK.\!Prove}
\NewAlgorithm{\PKverify}{PK.\!Verify}

We will rely on the Schnorr identification scheme~\cite{Schnorr}, which in its 
original form can be written as \(\PK[\alpha][A = g^\alpha]\).
The generalized form would be \(\PK[\alpha_1, \dotsc, \alpha_n][A = 
    \prod_{i=1}^n g_i^{\alpha_i}]\).
This could equivalently be written as
\begin{equation*}
  \PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i] \leftrightarrow
  \PKverify[\{g_i\}_i, q, A],
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (1) or reject (0).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
We also note that
\begin{multline*}
  \PK[\alpha, \beta][A = g^\alpha \land B = g^\beta] = \\
  \PK[\alpha][A = g^\alpha] \land \PK[\beta][B = g^\beta],
\end{multline*}
however, the challenge \(c\) must be the same in both sub-protocols.

\begin{figure*}
  \centering
  \begin{tabular}{lcl}
    \(\PKprove[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
    &
    & \(\PKverify[\{g_i\}_{i=1}^n, q, A]\):
    \\
    \midrule

    \(\forall i, 1\leq i\leq n\colon \rho_i\rgets \Z_q\)
    &
    &
    \\

@@

    \(1\leq i\leq n\colon s_i\gets \rho_i - c\alpha_i \mod q\)
    & \(\ProtoSendRight{\{s_i\}_{i=1}^n}\)
    &
    \\

@@

  \end{tabular}
  \caption{%
    \(\PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1]^n g_i^{\alpha_i}}\) using 
    the Schnorr identification scheme.
  }%
  \label{PKalgorithms}
\end{figure*}

@@

\NewAlgorithm{\SPKprove}{SPK.\!Prove}
\NewAlgorithm{\SPKverify}{SPK.\!Verify}

@@

\begin{figure*}
  \begin{minipage}[t]{0.49\linewidth}
    \begin{algorithmic}
      \Function{$\SPKprove$}{$\{g_i\}_i, q, A, \{\alpha_i\}_i, m$}
        \State{\(\forall i, 1\leq i\leq n\colon \rho_i\rgets \Z_q\)}
        \State{\(R\gets \prod_{i=1}^n g_i^{\rho_i}\)}
        \State{$c \gets H(\{g_i\}_i|A|R|m)$}
        \For{$1\leq i\leq n$}
          \State{$s_i \gets \rho_i - c\alpha_i \mod q$}
        \EndFor{}
        \State{\Return{$(\{s_i\}_i, c)$}}
      \EndFunction{}
    \end{algorithmic}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.49\linewidth}
    \begin{algorithmic}
      \Function{$\SPKverify$}{$\{g_i\}_i, q, A, m, \{s_i\}_i, c$}
        \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
        \If{$c = H(\{g_i\}_i|A|\hat R|m)$}
          \State{\Return{1}}
        \Else{}
          \State{\Return{0}}
        \EndIf{}
      \EndFunction{}
    \end{algorithmic}
  \end{minipage}
  \caption{%
    \(\SPK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}][m]\) 
    using the Fiat-Shamir heuristic on the Schnorr identification scheme.
  }%
  \label{SPKalgorithms}
\end{figure*}

>>>>

\paragraph*{Instantiations of the \acs{ZKPK} protocols}

For the convenience of the reader, we summarize 
(from~\cite{Camenisch-phdthesis}) how to instantiate general \acp{ZKPK} for 
discrete logarithms based on the Schnorr identification scheme~\cite{Schnorr}, 
which, in its original form, can be written as \(\PK[\alpha][A = g^\alpha]\).
The generalized form would be \(\PK[\alpha_1, \dotsc, \alpha_n][A = 
    \prod_{i=1}^n g_i^{\alpha_i}]\).
This could equivalently be written as
\begin{equation*}
  \Proto%
  {\PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i]}%
  {\PKverify[\{g_i\}_i, q, A]},
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (\(\top\)) or reject (\(\bot\)).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
We also note that
\begin{multline*}
  \PK[\alpha, \beta][A = g^\alpha \land B = g^\beta] = \\
  \PK[\alpha][A = g^\alpha] \land \PK[\beta][B = g^\beta],
\end{multline*}
however, the challenge \(c\) must be the same in both sub-protocols.

\begin{figure*}
  %\centering
  \small
  \begin{tabular}{lcl}
    \(\PKprove[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
    &
    & \(\PKverify[\{g_i\}_{i=1}^n, q, A]\):
    \\
    \midrule

    \(\forall i, 1\leq i\leq n\colon \rho_i\rgets \ZZ_q\)
    &
    &
    \\

@@

    \(\forall i\colon s_i\gets \rho_i - c\alpha_i \mod q\)
    & \(\ProtoSendRight{\{s_i\}_{i=1}^n}\)
    &
    \\

@@

  \end{tabular}
  \caption{%
    \(\PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}]\) using 
    the Schnorr identification scheme.
  }%
  \label{PKalgorithms}
\end{figure*}

@@

@@

\begin{figure}
  \small
  \begin{algorithmic}
    \Function{$\SPKprove$}{$\{g_i\}_i, q, A, \{\alpha_i\}_i, m$}
      \State{\(\forall i, 1\leq i\leq n\colon \rho_i\rgets \ZZ_q\)}
      \State{\(R\gets \prod_{i=1}^n g_i^{\rho_i}\)}
      \State{$c \gets H(\{g_i\}_i\concat A\concat R\concat m)$}
      \For{$1\leq i\leq n$}
        \State{$s_i \gets \rho_i - c\alpha_i \mod q$}
      \EndFor{}
      \State{\Return{$(\{s_i\}_i, c)$}}
    \EndFunction{}
  \end{algorithmic}

  \begin{algorithmic}
    \Function{$\SPKverify$}{$\{g_i\}_i, q, A, m, \{s_i\}_i, c$}
      \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
      \If{$c = H(\{g_i\}_i\concat A\concat \hat R\concat m)$}
        \State{\Return{$\top$}}
      \EndIf{}
      \State{\Return{$\bot$}}
    \EndFunction{}
  \end{algorithmic}
  \caption{%
    \(\SPK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}][m]\) 
    using the Fiat-Shamir heuristic on the Schnorr identification scheme.
  }%
  \label{SPKalgorithms}
\end{figure}
